# Comparative Metabolic Flux Analysis between Human and Mouse Models

## Introduction

This notebook presents a comparative analysis of metabolic fluxes between human adrenocortical carcinoma (ACC) samples and a mouse BPCre tumor model. The analysis involves calculating metabolic reaction activity scores (MRAS), computing metabolic fluxes, and performing comparative analyses across different metabolic pathways and subsystems.

---

## 1. Load Necessary Packages and Set Up Environment

```{r}
# Install necessary packages (execute only once)
# install.packages(c("METAFlux", "ggplot2", "dplyr", "pheatmap", "reshape2",
#                    "readr", "tidyr", "clusterProfiler", "DESeq2",
#                    "org.Hs.eg.db", "org.Mm.eg.db", "caret", "e1071",
#                    "igraph", "stringr", "homologene", "gt", "webshot2"))
# webshot2::install_phantomjs()  # Necessary for saving tables as images

# Set the working directory (adjust as necessary)
setwd("C:/Users/bruep/OneDrive/Área de Trabalho/Kleiton/METAFlux/Metaflux_update")

# Load packages
library(METAFlux)
library(ggplot2)
library(dplyr)
library(pheatmap)
library(reshape2)
library(readr)
library(tidyr)
library(clusterProfiler)
library(DESeq2)
library(org.Hs.eg.db)
library(org.Mm.eg.db)
library(caret)
library(e1071)
library(igraph)
library(stringr)    # For string manipulation
library(homologene) # For gene mapping between species
library(gt)         # For creating and exporting tables
library(webshot2)   # For saving tables as images

# Check if PhantomJS is installed (necessary for webshot2)
# If not installed, uncomment the line below:
# webshot2::install_phantomjs()

# Define auxiliary function for normalization (cubic root)
cbrt <- function(x) {
  sign(x) * abs(x)^(1/3)
}
```

---

## 2. Load Data

### 2.1. Load Human and Mouse Expression Data

```{r}
# Load human data - ACC (TCGA and ACC-COC3)
human_tcga_coc3 <- read.delim("TCGA-COC3_data.txt", row.names = 1)

# Load mouse data - BPCre model (tumor)
mouse_bpcre <- read.delim("BPCre_data.txt", row.names = 1)

# Check dimensions of the data
dim(human_tcga_coc3)
dim(mouse_bpcre)

# Ensure there are no negative values in the expression data
# Replace negative values with zero (if any)
human_tcga_coc3[human_tcga_coc3 < 0] <- 0
mouse_bpcre[mouse_bpcre < 0] <- 0
```

---

## 3. Calculate MRAS and Metabolic Fluxes

### 3.1. Calculate MRAS and Fluxes for Human Data

```{r}
# Calculate MRAS for human data
scores_tcga <- calculate_reaction_score(human_tcga_coc3)

# Calculate metabolic fluxes for human data
data("human_blood")  # Load the metabolic medium
flux_tcga <- compute_flux(mras = scores_tcga, medium = human_blood)
flux_tcga <- cbrt(flux_tcga)  # Apply cubic root normalization
```

### 3.2. Calculate MRAS and Fluxes for Mouse Data

```{r}
# Calculate MRAS for mouse data
scores_bpcre <- calculate_reaction_score(mouse_bpcre)

# Calculate metabolic fluxes for mouse data
flux_bpcre <- compute_flux(mras = scores_bpcre, medium = human_blood)
flux_bpcre <- cbrt(flux_bpcre)  # Apply cubic root normalization
```

---

## 4. Comparative Analysis of Metabolic Fluxes

### 4.1. Overall Comparison of Metabolic Fluxes

```{r}
# Load metabolic reaction information
data("human_gem")

# Find common reactions between human and mouse
common_reactions <- intersect(rownames(flux_tcga), rownames(flux_bpcre))

# Filter fluxes for common reactions
flux_tcga_common <- flux_tcga[common_reactions, ]
flux_bpcre_common <- flux_bpcre[common_reactions, ]

# Calculate mean fluxes for each group
mean_flux_tcga <- rowMeans(flux_tcga_common)
mean_flux_bpcre <- rowMeans(flux_bpcre_common)

# Create data frames for comparison
df_human <- data.frame(
  Reaction_ID = names(mean_flux_tcga),
  Mean_Flux_Human = mean_flux_tcga
)

df_mouse <- data.frame(
  Reaction_ID = names(mean_flux_bpcre),
  Mean_Flux_Mouse = mean_flux_bpcre
)

# Combine data frames by Reaction_ID
df_combined <- merge(df_human, df_mouse, by = "Reaction_ID")

# Calculate correlation between mean fluxes
correlation <- cor(df_combined$Mean_Flux_Human, df_combined$Mean_Flux_Mouse, method = "spearman")

# Display the correlation
print(paste("Spearman correlation between human and mouse mean fluxes:", round(correlation, 3)))

# Visualize the relationship between mean fluxes
p1 <- ggplot(df_combined, aes(x = Mean_Flux_Human, y = Mean_Flux_Mouse)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(
    title = paste("Figure 1: Comparison of Mean Metabolic Fluxes\nSpearman Correlation:", round(correlation, 3)),
    x = "Mean Flux (Human: ACC)",
    y = "Mean Flux (Mouse: BPCre)"
  ) +
  theme_bw()  # White background

# Display the plot
print(p1)

# Save the plot in high quality
ggsave("Figure1_Mean_Fluxes.png", plot = p1, width = 8, height = 6, dpi = 300, bg = "white")
```

---

## 5. Metabolic Pathway Analysis

### 5.1. Function to Calculate Pathway Activity

```{r}
# Define function to calculate activity per metabolic pathway
calculate_pathway_activity <- function(flux_data, gem_data) {
  pathways <- unique(gem_data$SUBSYSTEM)
  pathway_activity <- data.frame(Pathway = pathways, Activity = NA)
  
  for (i in seq_along(pathways)) {
    pathway <- pathways[i]
    reactions_in_pathway <- gem_data$ID[gem_data$SUBSYSTEM == pathway]
    reactions_in_flux <- intersect(reactions_in_pathway, rownames(flux_data))
    if (length(reactions_in_flux) > 0) {
      # Ensure the result is a matrix
      activity <- rowMeans(abs(flux_data[reactions_in_flux, , drop = FALSE]))
      pathway_activity$Activity[i] <- mean(activity, na.rm = TRUE)
    } else {
      pathway_activity$Activity[i] <- NA
    }
  }
  
  return(pathway_activity)
}
```

### 5.2. Calculate Pathway Activity for Each Group

```{r}
# Calculate pathway activity for human data
pathway_activity_tcga <- calculate_pathway_activity(flux_tcga, human_gem)

# Calculate pathway activity for mouse data
pathway_activity_bpcre <- calculate_pathway_activity(flux_bpcre, human_gem)

# Combine human and mouse pathway activities
pathway_activity_combined <- merge(pathway_activity_tcga, pathway_activity_bpcre, by = "Pathway", suffixes = c("_Human", "_Mouse"))

# Calculate correlation between pathway activities
correlation_pathways <- cor(pathway_activity_combined$Activity_Human, pathway_activity_combined$Activity_Mouse, method = "spearman", use = "complete.obs")

# Display the correlation
print(paste("Spearman correlation of pathway activities:", round(correlation_pathways, 3)))

# Visualize the relationship
p2 <- ggplot(pathway_activity_combined, aes(x = Activity_Human, y = Activity_Mouse)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(
    title = paste("Figure 2: Comparison of Metabolic Pathway Activities\nSpearman Correlation:", round(correlation_pathways, 3)),
    x = "Activity (Human: ACC)",
    y = "Activity (Mouse: BPCre)"
  ) +
  theme_bw()  # White background

# Display the plot
print(p2)

# Save the plot in high quality
ggsave("Figure2_Pathway_Activity.png", plot = p2, width = 8, height = 6, dpi = 300, bg = "white")
```

---

## 6. Correlation Analysis of Specific Metabolic Pathways

### 6.1. Analysis for "Steroid metabolism"

```{r}
# Define pathway of interest
pathway_of_interest <- "Steroid metabolism"

# Get reactions in this pathway
reactions_in_pathway <- human_gem$ID[human_gem$SUBSYSTEM == pathway_of_interest]

# Check if reactions exist
if (length(reactions_in_pathway) > 0) {
  # Extract fluxes for humans
  flux_human_pathway <- flux_tcga[reactions_in_pathway, , drop = FALSE]
  
  # Extract fluxes for mice
  flux_mouse_pathway <- flux_bpcre[reactions_in_pathway, , drop = FALSE]
  
  # Ensure reactions exist in both datasets
  common_reactions <- intersect(rownames(flux_human_pathway), rownames(flux_mouse_pathway))
  
  flux_human_pathway <- flux_human_pathway[common_reactions, , drop = FALSE]
  flux_mouse_pathway <- flux_mouse_pathway[common_reactions, , drop = FALSE]
  
  # Calculate correlation for each reaction
  correlation_results <- data.frame(
    Reaction_ID = common_reactions,
    Correlation = NA,
    P_value = NA,
    Method = "Spearman",
    stringsAsFactors = FALSE
  )
  
  for (i in seq_along(common_reactions)) {
    reaction <- common_reactions[i]
    
    # Human fluxes for the reaction
    human_fluxes <- as.numeric(flux_human_pathway[reaction, ])
    
    # Mouse fluxes for the reaction
    mouse_fluxes <- as.numeric(flux_mouse_pathway[reaction, ])
    
    # Combine fluxes using the smallest sample size (samples are not paired)
    min_samples <- min(length(human_fluxes), length(mouse_fluxes))
    human_fluxes <- human_fluxes[1:min_samples]
    mouse_fluxes <- mouse_fluxes[1:min_samples]
    
    # Calculate Spearman correlation
    cor_test <- cor.test(human_fluxes, mouse_fluxes, method = "spearman")
    
    # Store the results
    correlation_results$Correlation[i] <- cor_test$estimate
    correlation_results$P_value[i] <- cor_test$p.value
  }
  
  # Order by highest absolute correlations
  correlation_results <- correlation_results[order(-abs(correlation_results$Correlation)), ]
  
  # Select the top 30 reactions
  top_30_correlations <- head(correlation_results, 30)
  
  # Add reaction information
  top_30_correlations <- merge(top_30_correlations, human_gem[, c("ID", "EQUATION", "SUBSYSTEM")],
                               by.x = "Reaction_ID", by.y = "ID", all.x = TRUE)
  
  # Visualize the table using 'gt'
  tabela_gt1 <- top_30_correlations %>%
    gt() %>%
    tab_header(
      title = md(paste("**Table:** Top 30 Reactions in Pathway", pathway_of_interest)),
      subtitle = "Highest Correlations between Human and Mouse Fluxes"
    ) %>%
    fmt_number(
      columns = c("Correlation", "P_value"),
      decimals = 3
    ) %>%
    data_color(
      columns = "Correlation",
      colors = scales::col_numeric(
        palette = c("red", "white", "blue"),
        domain = c(-1, 1)
      )
    ) %>%
    cols_label(
      Reaction_ID = "Reaction ID",
      Correlation = "Correlation",
      P_value = "P-value",
      Method = "Method",
      EQUATION = "Equation",
      SUBSYSTEM = "Subsystem"
    ) %>%
    tab_options(
      table.background.color = "white"
    )
  
  # Display the table
  print(tabela_gt1)
  
  # Save the table as a PNG image
  gtsave(tabela_gt1, "Table_Top30_Reactions_Specific_Pathway.png")
  
} else {
  print(paste("No reactions found for the pathway:", pathway_of_interest))
}
```

---

## 7. Advanced Clustering and Visualization

### 7.1. Principal Component Analysis (PCA)

```{r}
# Combine fluxes for humans and mice
combined_flux <- cbind(flux_tcga, flux_bpcre)

# Transpose to have samples in rows
combined_flux_t <- t(combined_flux)

# Scale the data
combined_flux_scaled <- scale(combined_flux_t)

# Remove columns with zero variance or all NA values
zero_var_columns <- apply(combined_flux_scaled, 2, function(x) {
  var_x <- var(x, na.rm = TRUE)
  is.na(var_x) || var_x == 0  # Check if variance is NA or zero
})

if (any(zero_var_columns)) {
  combined_flux_scaled <- combined_flux_scaled[, !zero_var_columns]
}

# Perform PCA
pca_result <- prcomp(combined_flux_scaled, center = TRUE)

# Create a data frame with PCA results
pca_df <- data.frame(pca_result$x)
pca_df$Group <- c(rep("Human_Tumor", ncol(flux_tcga)),
                  rep("Mouse_BPCre", ncol(flux_bpcre)))

# Visualize the first two principal components
p4 <- ggplot(pca_df, aes(x = PC1, y = PC2, color = Group)) +
  geom_point(size = 2) +
  labs(
    title = "Figure 4: PCA Analysis of Metabolic Fluxes",
    x = "PC1",
    y = "PC2"
  ) +
  theme_bw()  # White background

# Display the plot
print(p4)

# Save the plot in high quality
ggsave("Figure4_PCA_Metabolic_Fluxes.png", plot = p4, width = 8, height = 6, dpi = 300, bg = "white")
```

---

## 8. Correlation Analysis for All Reactions

### 8.1. Correlation of All Fluxes between Human and Mouse

```{r}
# Extract fluxes for humans (tumor samples)
flux_human_all <- flux_tcga

# Extract fluxes for mice (tumor samples)
flux_mouse_all <- flux_bpcre

# Find common reactions between human and mouse
common_reactions <- intersect(rownames(flux_human_all), rownames(flux_mouse_all))

# Filter fluxes for common reactions
flux_human_all <- flux_human_all[common_reactions, , drop = FALSE]
flux_mouse_all <- flux_mouse_all[common_reactions, , drop = FALSE]

# Initialize data frame to store results
correlation_results_all <- data.frame(
  Reaction_ID = common_reactions,
  Correlation = NA,
  P_value = NA,
  Method = "Spearman",
  stringsAsFactors = FALSE
)

# Calculate correlation for each reaction
for (i in seq_along(common_reactions)) {
  reaction <- common_reactions[i]
  
  # Human fluxes for the reaction
  human_fluxes <- as.numeric(flux_human_all[reaction, ])
  
  # Mouse fluxes for the reaction
  mouse_fluxes <- as.numeric(flux_mouse_all[reaction, ])
  
  # Combine fluxes using the smallest sample size (samples are not paired)
  min_samples <- min(length(human_fluxes), length(mouse_fluxes))
  human_fluxes <- human_fluxes[1:min_samples]
  mouse_fluxes <- mouse_fluxes[1:min_samples]
  
  # Calculate Spearman correlation
  cor_test <- cor.test(human_fluxes, mouse_fluxes, method = "spearman")
  
  # Store the results
  correlation_results_all$Correlation[i] <- cor_test$estimate
  correlation_results_all$P_value[i] <- cor_test$p.value
}

# Order by highest absolute correlations
correlation_results_all <- correlation_results_all[order(-abs(correlation_results_all$Correlation)), ]

# Select the top 30 reactions
top_30_correlations_all <- head(correlation_results_all, 30)

# Add reaction information
top_30_correlations_all <- merge(top_30_correlations_all, human_gem[, c("ID", "EQUATION", "SUBSYSTEM")],
                                 by.x = "Reaction_ID", by.y = "ID", all.x = TRUE)

# Reorder the columns
top_30_correlations_all <- top_30_correlations_all[, c("Reaction_ID", "Correlation", "P_value", "Method", "EQUATION", "SUBSYSTEM")]

# Visualize the table using 'gt'
tabela_gt2 <- top_30_correlations_all %>%
  gt() %>%
  tab_header(
    title = md("**Table:** Top 30 Reactions with Highest Correlations"),
    subtitle = "Between Human and Mouse Fluxes"
  ) %>%
  fmt_number(
    columns = c("Correlation", "P_value"),
    decimals = 3
  ) %>%
  data_color(
    columns = "Correlation",
    colors = scales::col_numeric(
      palette = c("red", "white", "blue"),
      domain = c(-1, 1)
    )
  ) %>%
  cols_label(
    Reaction_ID = "Reaction ID",
    Correlation = "Correlation",
    P_value = "P-value",
    Method = "Method",
    EQUATION = "Equation",
    SUBSYSTEM = "Subsystem"
  ) %>%
  tab_options(
    table.background.color = "white"
  )

# Display the table
print(tabela_gt2)

# Save the table as a PNG image
gtsave(tabela_gt2, "Table_Top30_Correlations_All_Reactions.png")

# Optional: Save the table as a CSV file
write.csv(top_30_correlations_all, file = "Top30_Correlations_flux_tcga_flux_bpcre.csv", row.names = FALSE)

# Create a heatmap of the correlations of the top 30 reactions and save in high quality
correlation_matrix <- as.matrix(top_30_correlations_all$Correlation)
rownames(correlation_matrix) <- top_30_correlations_all$Reaction_ID

# Save the heatmap with a white background
png("Heatmap_Top30_Correlations.png", width = 800, height = 1000, res = 150, bg = "white")
pheatmap(correlation_matrix, cluster_rows = FALSE, cluster_cols = FALSE,
         main = "Heatmap of Correlations of Top 30 Reactions between flux_tcga and flux_bpcre")
dev.off()
```

---

## 9. Comparative Analysis for Specific Subsystems

### 9.1. Analysis for "Pyrimidine metabolism"

```{r}
# Define the subsystem of interest
subsystem_of_interest <- "Pyrimidine metabolism"

# Get reactions in this subsystem
reactions_in_subsystem <- human_gem$ID[human_gem$SUBSYSTEM == subsystem_of_interest]

# Find common reactions in the subsystem between human and mouse
common_reactions <- intersect(rownames(flux_tcga), rownames(flux_bpcre))
common_reactions_in_subsystem <- intersect(common_reactions, reactions_in_subsystem)

# Check if reactions exist
if(length(common_reactions_in_subsystem) > 0) {
  # Filter fluxes for common reactions in the subsystem
  flux_tcga_common <- flux_tcga[common_reactions_in_subsystem, ]
  flux_bpcre_common <- flux_bpcre[common_reactions_in_subsystem, ]

  # Calculate mean fluxes for each group
  mean_flux_tcga <- rowMeans(flux_tcga_common)
  mean_flux_bpcre <- rowMeans(flux_bpcre_common)

  # Create data frames for comparison
  df_human <- data.frame(
    Reaction_ID = names(mean_flux_tcga),
    Mean_Flux_Human = mean_flux_tcga
  )

  df_mouse <- data.frame(
    Reaction_ID = names(mean_flux_bpcre),
    Mean_Flux_Mouse = mean_flux_bpcre
  )

  # Combine data frames by Reaction_ID
  df_combined <- merge(df_human, df_mouse, by = "Reaction_ID")

  # Calculate correlation between mean fluxes and p-value
  cor_test <- cor.test(df_combined$Mean_Flux_Human, df_combined$Mean_Flux_Mouse, method = "spearman")
  correlation <- cor_test$estimate
  p_value <- cor_test$p.value

  # Display the correlation and p-value
  print(paste("Spearman correlation between human and mouse mean fluxes in subsystem", subsystem_of_interest, ":", round(correlation, 3)))
  print(paste("P-value:", signif(p_value, 3)))

  # Visualize the relationship between mean fluxes
  p_subsystem <- ggplot(df_combined, aes(x = Mean_Flux_Human, y = Mean_Flux_Mouse)) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "lm", se = FALSE, color = "red") +
    labs(
      title = paste("Figure: Comparison of Mean Fluxes in Subsystem", subsystem_of_interest),
      subtitle = paste("Spearman Correlation:", round(correlation, 3), "| P-value:", format.pval(p_value, digits=2, eps=0.001)),
      x = "Mean Flux (Human: ACC)",
      y = "Mean Flux (Mouse: BPCre)"
    ) +
    theme_bw()  # White background

  # Display the plot
  print(p_subsystem)

  # Save the plot in high quality
  ggsave("Figure_Mean_Fluxes_Pyrimidine_Metabolism.png", plot = p_subsystem, width = 8, height = 6, dpi = 300, bg = "white")

} else {
  print(paste("No common reactions found in the subsystem:", subsystem_of_interest))
}
```

### 9.2. Analysis for "Arginine and proline metabolism"

```{r}
# Define the subsystem of interest
subsystem_of_interest <- "Arginine and proline metabolism"

# Get reactions in this subsystem
reactions_in_subsystem <- human_gem$ID[human_gem$SUBSYSTEM == subsystem_of_interest]

# Find common reactions in the subsystem between human and mouse
common_reactions <- intersect(rownames(flux_tcga), rownames(flux_bpcre))
common_reactions_in_subsystem <- intersect(common_reactions, reactions_in_subsystem)

# Check if reactions exist
if(length(common_reactions_in_subsystem) > 0) {
  # Filter fluxes for common reactions in the subsystem
  flux_tcga_common <- flux_tcga[common_reactions_in_subsystem, ]
  flux_bpcre_common <- flux_bpcre[common_reactions_in_subsystem, ]

  # Calculate mean fluxes for each group
  mean_flux_tcga <- rowMeans(flux_tcga_common)
  mean_flux_bpcre <- rowMeans(flux_bpcre_common)

  # Create data frames for comparison
  df_human <- data.frame(
    Reaction_ID = names(mean_flux_tcga),
    Mean_Flux_Human = mean_flux_tcga
  )

  df_mouse <- data.frame(
    Reaction_ID = names(mean_flux_bpcre),
    Mean_Flux_Mouse = mean_flux_bpcre
  )

  # Combine data frames by Reaction_ID
  df_combined <- merge(df_human, df_mouse, by = "Reaction_ID")

  # Calculate correlation between mean fluxes and p-value
  cor_test <- cor.test(df_combined$Mean_Flux_Human, df_combined$Mean_Flux_Mouse, method = "spearman")
  correlation <- cor_test$estimate
  p_value <- cor_test$p.value

  # Display the correlation and p-value
  print(paste("Spearman correlation between human and mouse mean fluxes in subsystem", subsystem_of_interest, ":", round(correlation, 3)))
  print(paste("P-value:", signif(p_value, 3)))

  # Visualize the relationship between mean fluxes
  p_subsystem <- ggplot(df_combined, aes(x = Mean_Flux_Human, y = Mean_Flux_Mouse)) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "lm", se = FALSE, color = "blue") +
    labs(
      title = paste("Figure: Comparison of Mean Fluxes in Subsystem", subsystem_of_interest),
      subtitle = paste("Spearman Correlation:", round(correlation, 3), "| P-value:", format.pval(p_value, digits=2, eps=0.001)),
      x = "Mean Flux (Human: ACC)",
      y = "Mean Flux (Mouse: BPCre)"
    ) +
    theme_bw()  # White background

  # Display the plot
  print(p_subsystem)

  # Save the plot in high quality
  ggsave("Figure_Mean_Fluxes_Arginine_Proline_Metabolism.png", plot = p_subsystem, width = 8, height = 6, dpi = 300, bg = "white")

} else {
  print(paste("No common reactions found in the subsystem:", subsystem_of_interest))
}
```

### 9.3. Analysis for "Alanine, aspartate and glutamate metabolism"

```{r}
# Define the subsystem of interest
subsystem_of_interest <- "Alanine, aspartate and glutamate metabolism"

# Get reactions in this subsystem
reactions_in_subsystem <- human_gem$ID[human_gem$SUBSYSTEM == subsystem_of_interest]

# Find common reactions in the subsystem between human and mouse
common_reactions <- intersect(rownames(flux_tcga), rownames(flux_bpcre))
common_reactions_in_subsystem <- intersect(common_reactions, reactions_in_subsystem)

# Check if reactions exist
if(length(common_reactions_in_subsystem) > 0) {
  # Filter fluxes for common reactions in the subsystem
  flux_tcga_common <- flux_tcga[common_reactions_in_subsystem, ]
  flux_bpcre_common <- flux_bpcre[common_reactions_in_subsystem, ]

  # Calculate mean fluxes for each group
  mean_flux_tcga <- rowMeans(flux_tcga_common)
  mean_flux_bpcre <- rowMeans(flux_bpcre_common)

  # Create data frames for comparison
  df_human <- data.frame(
    Reaction_ID = names(mean_flux_tcga),
    Mean_Flux_Human = mean_flux_tcga
  )

  df_mouse <- data.frame(
    Reaction_ID = names(mean_flux_bpcre),
    Mean_Flux_Mouse = mean_flux_bpcre
  )

  # Combine data frames by Reaction_ID
  df_combined <- merge(df_human, df_mouse, by = "Reaction_ID")

  # Calculate correlation between mean fluxes and p-value
  cor_test <- cor.test(df_combined$Mean_Flux_Human, df_combined$Mean_Flux_Mouse, method = "spearman")
  correlation <- cor_test$estimate
  p_value <- cor_test$p.value

  # Display the correlation and p-value
  print(paste("Spearman correlation between human and mouse mean fluxes in subsystem", subsystem_of_interest, ":", round(correlation, 3)))
  print(paste("P-value:", signif(p_value, 3)))

  # Visualize the relationship between mean fluxes
  p_subsystem <- ggplot(df_combined, aes(x = Mean_Flux_Human, y = Mean_Flux_Mouse)) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "lm", se = FALSE, color = "green") +
    labs(
      title = paste("Figure: Comparison of Mean Fluxes in Subsystem", subsystem_of_interest),
      subtitle = paste("Spearman Correlation:", round(correlation, 3), "| P-value:", format.pval(p_value, digits=2, eps=0.001)),
      x = "Mean Flux (Human: ACC)",
      y = "Mean Flux (Mouse: BPCre)"
    ) +
    theme_bw()  # White background

  # Display the plot
  print(p_subsystem)

  # Save the plot in high quality
  ggsave("Figure_Mean_Fluxes_Alanine_Aspartate_Glutamate_Metabolism.png", plot = p_subsystem, width = 8, height = 6, dpi = 300, bg = "white")

} else {
  print(paste("No common reactions found in the subsystem:", subsystem_of_interest))
}
```
